---
title: "Reproducible Pitch"
author: "Enchantment"
date: "1.2.2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```


 
## Requirements

OK, you've made your shiny app, now it's time to make your pitch. You get 5 slides (inclusive of the title slide) to pitch a your app. You're going to create a web page using Slidify or Rstudio Presenter with an html5 slide deck.

Here's what you need

5 slides to pitch our idea done in Slidify or Rstudio Presenter
Your presentation pushed to github or Rpubs
A link to your github or Rpubs presentation pasted into the provided text box
Your presentation must satisfy the following

It must be done in Slidify or Rstudio Presenter
It must be 5 pages
It must be hosted on github or Rpubs
It must contained some embedded R code that gets run when slidifying the document

## Single Variable Scatter vs Infant Mortality (boxplot)
#### Use a scatter/boxplot to explore each parameter and its relationship with Infant Mortality
```{r scatter, echo = FALSE, message=FALSE}
library(datasets)
swdata <- swiss
boxplot(Infant.Mortality ~ Agriculture, 
            data = swdata)
```

## Single Variable Regression vs Infant Mortality (linear regression)
#### Use linear regression to explore each parameter and its relationship with Infant Mortality
```{r reg, echo = FALSE, message=FALSE}
library(datasets)
library(glmnet)
swdata <- swiss
model <- lm(Infant.Mortality ~ Agriculture, data=swdata)
par(mfrow = c(2,2))
plot(model)
```

## Lasso Use Case
#### Use Lasso Regression to determine feature importance and show those features to user:
```{r lasso, echo = FALSE, message=FALSE}

library(glmnet)
library(datasets)
library(corrplot)

swdata <- swiss

Xn <- swdata[, !names(swdata) %in% c("Infant.Mortality")]
yn <- swdata["Infant.Mortality"]

X <- as.matrix(Xn)  
y <- as.matrix(yn)


lambdas <- 10^seq(-5, 5, length.out = 100)

lasso_cv <- cv.glmnet(X, y, alpha = 1, lambda = lambdas,
                      standardize = TRUE, nfolds = 10)

lambda_cv <- lasso_cv$lambda.min

model_cv <- glmnet(X, y, alpha = 1,
                   lambda = lambda_cv, standardize = TRUE)

y_hat_cv <- predict(model_cv, X)
rsq_lasso_cv <- cor(y, y_hat_cv)^2
lasso_coef_shrink <- glmnet(X, y, alpha = 1, lambda = lambdas, standardize = FALSE)

lcs <- glmnet(X, y, alpha = 1, lambda = lambda_cv, standardize = FALSE)

coeffs <- coef(lcs)
df <- data.frame(name = coeffs@Dimnames[[1]][coeffs@i + 1], coefficient = coeffs@x)
df$abs <- abs(df$coefficient)
df[order(df$abs, decreasing=TRUE),]
```
#### Use lasso regression to fit model? (perhaps not for this model!)
#### R^2 below
```{r lasso fit, echo = FALSE, message=FALSE}
rsq_lasso_cv
```


